\chapter{Introduction}
\label{specification}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{The PARSE Project}
The overall project deliverable was to create a toolkit to measure and monitor body volumes, as well as limb circumferences and relative positions of ultrasound scanners on the surface of the body.\\ 

There were three key aims for the toolkit:\begin{itemize}
\item To offer a similar accuracy of volume measurement when compared to the BOD POD \cite{cosmed2013}, at a much lower cost 
\item To be able repeatedly measure limb circumferences 
\item To repeatedly position an ultrasound scanner without the use of an indelible mark\end{itemize}

The team was also required to provide an interface that would allow medical personnel to use the toolkit with ease.

\input{spec/stuff_from_spec}

\section{Project Customer}
The project team first approached the customer at the start of the project with a proposal for developing an innovative object sharing environment. Matt continued to support the PARSE project as the project evolved away from this initial idea and throughout the entire duration.\\ 

A former postgraduate Computer Science Research Assistant at the University of Warwick, Matt was considered appropriate for the role of project customer due to his experience authoring many academic publications, all of which required some degree of collaboration, which makes him familiar with the challenges and complications of working in teams and group work. He was also approached due to his friendly and easy going attitude.\\

\section{Project Deliverables}
The project deliverables were defined by the CS407 \cite{ouroboros2007} course structure. Therefore the deliverables were: \begin{itemize}

\item The \textb{Project Specification}: The specification was not marked as a separate component, but was a compulsory milestone that was required to be passed for the project to continue. It identified the planned activities and schedule for the remainder of the project. The document has been included in Appendix A.

\item \textb{Progress Presentation}:
The progress presentation took the form of a poster presentation during week 10, and counted for 10\% of the assessment. The poster is included in Appendix B and the accompanying slides are also included in Appendix B.

\item The \textb{PARSE Toolkit}: The substantial software outcome, specified by the Project Specification and described in full in this final report. The software itself carries no marks.

\item \textb{This Report}: Is jointly authored by the members of PARSE and counts for 60\% of the assessment. It's purpose is to document the process of delivering the agreed software, from both a technical and a process management standpoint. 

\item The \textb{Individual Report}s: Pieces of reflective writing which allows each group member to discuss their own contribution to the project, and what lessons they have learned from the process. It counts for 10\% of the assessment.

\item The \texb{Final Project Presentation}: Will count for the remaining 20\% of the assessment, allows the group to present their completed work to an audience, and allows members of the audience to question members of the group about their work. The group will be expected to demonstrate their software working.\end{itemize}

\pagebreak

\input{spec/requirements}